---
title: "Predicts Individual Life Satiafication by Demographic Characteristics"
author: "Heran Zhou, Xinyu Zhong, Yaqing Feng, Yuhan Gu"
date: "Octobor 19, 2020"

header-includes:
  - \usepackage{booktabs}
  - \usepackage{subfig}
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: false
---

<div align="center"> github: https://github.com/Kevinzhou0717/STA304-Problem-Set-2 </div>

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(dplyr)
library(survey)
library(pROC)
library(kableExtra)
#library(bookdown)
library(arsenal)
library(table1)
```

```{r echo=F, include=F}
gss <- read_csv('gss.csv')
raw_data <- read_csv("AA4uzB6k.csv")
```

# Abstract



# Introduction


# Data


```{r pairplot, fig.cap="Plot of raw data", echo=FALSE}
sub_plot <- raw_data %>% 
  select(agedc,slm_01,sex,prv,region,
         luc_rst,marstat, ehg3_01b,famincg2,
         odr_10,livarr12,uhw_16gr,lmam_01,srh_110) %>% 
  mutate_at(vars(agedc:srh_110), .funs = funs(ifelse(.>=96, NA, .))) 
# Fix the names
sub_plot <- sub_plot %>% 
  rename(age = agedc, feelings_life = slm_01,
         sex = sex, province = prv,
         region = region,pop_center = luc_rst,
         marital_status = marstat,education = ehg3_01b,
         income_family = famincg2,own_rent = odr_10,
         living_arrangement = livarr12,average_hours_worked = uhw_16gr,
         worked_last_week = lmam_01,self_rated_health = srh_110) 
sub_plot <- sub_plot %>%
  select(feelings_life, age, income_family, education, 
         marital_status, living_arrangement, self_rated_health)
sub_plot <- na.omit(sub_plot)
pairs(sub_plot)
```

Refer to Figure \@ref(fig:pairplot).\newline

```{r echo=F, include=F}
# select variable and change variable type
col.names <- colnames(gss[,c(12:24,27:62,64:81)])
gss[,col.names] <- lapply(gss[,col.names], as.factor)
data <- gss %>% 
  select(age, sex, income_family, place_birth_canada, region, 
           education, pop_center, feelings_life, marital_status, 
           living_arrangement, self_rated_health, income_respondent,
           self_rated_mental_health, religion_has_affiliation,
           children_in_household, number_marriages)
data <- na.omit(data)
summary(data)
glimpse(data)
```


```{r echo=F, include=F}
# reduce level of self_rated_health 
data$self_rated_health[data$self_rated_health[]=="Don't know"] <- "Fair"
data$self_rated_health[data$self_rated_health[]=="Very good"] <- "Good"
data$self_rated_health <- droplevels(data$self_rated_health)
# reduce level of education level
levels(data$education)[8:9] <- c("Bachelor or above",
                                  "college / below bachelor level")
data$education[data$education[]=="Bachelor's degree (e.g. B.A., B.Sc., LL.B.)"] <- "Bachelor or above"
data$education[data$education[]=="University certificate, diploma or degree above the bach..."] <- "Bachelor or above"
data$education[data$education[]=="University certificate or diploma below the bachelor's level"] <- "college / below bachelor level"
data$education[data$education[]=="College, CEGEP or other non-university certificate or di..."] <- "college / below bachelor level"
data$education[data$education[]=="Trade certificate or diploma"] <- "college / below bachelor level"
data$education <- droplevels(data$education)
# reduce level of living arrangement
levels(data$living_arrangement)[12:13] <- c("No spouse and children",
                                 "Spouse and children")

data$living_arrangement[data$living_arrangement[]=="No spouse and single child under 25 years of age" ]<-"No spouse and children"
data$living_arrangement[data$living_arrangement[]=="No spouse and single child 25 years of age or older" ]<-"No spouse and children"
data$living_arrangement[data$living_arrangement[]=="No spouse and non-single child(ren)" ]<-"No spouse and children"

data$living_arrangement[data$living_arrangement[]=="Spouse and single child under 25 years of age" ]<-"Spouse and children"
data$living_arrangement[data$living_arrangement[]=="Spouse and single child 25 years of age or older" ]<-"Spouse and children"
data$living_arrangement[data$living_arrangement[]=="Spouse and non-single child(ren)" ]<-"Spouse and children"
data$living_arrangement <- droplevels(data$living_arrangement)
# reduce level of pop_center
levels(data$pop_center)[4] <- c("Rural and non (CMA/CA) or Prince Edward Island")
data$pop_center[data$pop_center[]=="Prince Edward Island" ]<-"Rural and non (CMA/CA) or Prince Edward Island"
data$pop_center[data$pop_center[]=="Rural areas and small population centres (non CMA/CA)" ]<-"Rural and non (CMA/CA) or Prince Edward Island"
data$pop_center <- droplevels(data$pop_center)
# reduce level of income_family
levels(data$income_family)[7] <- "$50,000 to $124,999"
data$income_family[data$income_family[]=="$50,000 to $74,999"]<-"$50,000 to $124,999"
data$income_family[data$income_family[]=="$75,000 to $99,999"]<-"$50,000 to $124,999"
data$income_family[data$income_family[]=="$100,000 to $ 124,999"]<-"$50,000 to $124,999"
data$income_family <- droplevels(data$income_family)
```

```{r echo=F, include=F}
#for logistic model, divide feeling_of_life by mean
mean(data$feelings_life)
summary(as.factor(data$feelings_life))
data <- data %>% 
  mutate(life_satisfication = as.factor(ifelse(feelings_life>mean(feelings_life),'Higher','Lower')))
```

# Model

Hence, our model is 
\[
log(\frac{p}{1-p}) = \beta_0 +\beta_2x_1 +\beta_3x_2 +\beta_4x_3 +\beta_5x_4+\beta_6 x_5+\beta_7 x_6+ \epsilon
\]
where p represent the prebability to have life satisfaction below average. $x_i$(i=1,...,6) represent gender, education level, living area, family income, marital status and self_rated_health correspondingly, $\beta_i$(i=2,..,7) are estimate coefficient, $\beta_1$ is intercept, $\epsilon$ is random error.\par



# Results

```{r ech=F, include=F}
#split data for validation
set.seed(304)
# 60% observations in train dataset, 40% in test data set
smp_size <- floor(0.6 * nrow(data))
train_ind <- sample(seq_len(nrow(data)), size = smp_size)
train <- data[train_ind, ]
test <- data[-train_ind, ]
```


```{r echo=F, include=F}
# fit logistic model
N=35151728
n=length(train$life_satisfication)
fpc.srs = rep(N, n)
train.srs <- svydesign(id=~1, data=train, fpc=fpc.srs)
train.logit <- svyglm(life_satisfication ~ sex + education + pop_center +
                       marital_status + self_rated_health +income_family, 
                       train.srs, family="binomial")
summary(train.logit) 
# use test dataset to test validity
N=35151728	
n=length(test$life_satisfication)
fpc.srs = rep(N, n)
test.srs <- svydesign(id=~1, data=test, fpc=fpc.srs)
test.logit <- svyglm(life_satisfication ~ sex + education + pop_center +
                       marital_status + self_rated_health + income_family, 
                       test.srs, family="binomial")
summary(test.logit)
```


```{r tab1}
beta1 <- coef(train.logit)
beta2 <- coef(test.logit)
SD <-  summary(train.logit)$coef[,2]
p_value = format(summary(train.logit)$coef[,4], scientific = TRUE, digits = 4)
# table of coefficient
kable(cbind(round(exp(beta2),3), round(exp(beta1),3),
            round(exp(SD),3), p_value),
      col.names = c('test','train', 'SD','P value'),
      booktabs = TRUE,
      caption = "Summary of Model")
```

As shown in Figure \@ref(fig:ROC), the predictive of final model is 0.69 which is considered acceptable.

Table \@ref(tab:tab1).

```{r ROC, fig.cap="ROC curve", echo=F}
#ROC curve
roc_p <- predict(train.logit, type = "response")
roc_l <- roc(train$life_satisfication ~ roc_p)
## Setting levels: control = 0, case = 1
## Setting direction: controls < cases
## The True Positive Rate ##
TPR <- roc_l$sensitivities
## The False Positive Rate ##
FPR <- 1 - roc_l$specificities
roc <- data.frame(FPR,TPR)
#ROC curve
ggplot(roc, aes(FPR,TPR)) + 
  geom_line(size = 2, alpha = 0.7,col='red') +
  geom_segment(aes(x = 0, xend = 1, y = 0, yend = 1), linetype="dashed") +
  labs(x = "False Positive Rate (1-Specificity)", 
       y = "True Positive Rate (Sensitivity)") +
  annotate("text", x = 0.75, y = 0.5, vjust = 0, 
           label = paste("AUC =",round(auc(roc_l),2)))
```



# Discussion



## Weaknesses


## Next Steps



# References

# Appendix


```{r datasummary, echo = F,  results="asis"}
tt <- gss %>% 
  select(age, sex, feelings_life, place_birth_canada,  
         vis_minority, citizenship_status, own_rent,income_family, 
         education, pop_center, marital_status, 
         living_arrangement, self_rated_health, 
         self_rated_mental_health, religion_has_affiliation,
         children_in_household, number_marriages)
table_one <- tableby(gss$region ~ ., data = tt)
summary(table_one, title = "Summary of Data")
```

