---
title: "Predicts Individual Life Satiafication by Demographic Characteristics"
author: "Heran Zhou, Xinyu Zhong, Yuhan Gu"
date: '2020-10-19'
output: pdf_document
---
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(dplyr)
library(survey)
library(pROC)
library(kableExtra)
library(arsenal)
library(table1)
library(gtsummary)
```

```{r echo=F, include=F}
gss <- read_csv('gss.csv')
glimpse(gss)
col.names <- colnames(gss[,c(12:24,27:62,64:81)])
gss[,col.names] <- lapply(gss[,col.names], as.factor)
```

## Title of your Report

# Name(s) of Author(s) 
# Date

## Abstract

Here is where you give a brief (one paragraph overview of your entire paper). This should include some background/introduction, some methodology, results and conclusions.

## Introduction

Here is where you should give insight into the setting and introduce the goal of the analysis. Here you can introduce ideas and basic concepts regarding the study setting and the potential model. Again, this is the introduction, so you should be explaining the importance of the work that is ahead and hopefully build some suspense for the reader. You can also highlight what will be included in the subsequent sections.

## Data

Introduce the data, explain why it was selected. Make sure to comment on important features and highlight any potential drawbacks to the data.



For better summarization and interpretation, we reduced level of some categorical variable by merge their similar level to the same level or new level. 

For the self-rated health variable, the level of “Don’t know” has been merged to the existing level of “Fair” and , the level of “Very good” has been merged to the existing level of “Good”;
For the education variable, 2 new levels,  “Bachelor or above” and “college/below bachelor level”, are created. The level of “Bachelor’s degree(e.g. B.A., B.Sc., LL.B.)” and “University certificate, diploma or degree above the bach…” have been merged to the level of  “Bachelor or above” and  the level of “University certificate, diploma or degree below the bachelor’s level” and “College, CEGEP or other non-university certificate or di…” and “Trade certificate or diploma” have been merged to the level of “college/below bachelor level”;
For the pop_center variable, a new level “Rural and non (CMA/CA) or Prince Edward Island” is created. The level of “Prince Edward Island” and “Rural areas and small population centres(non CMA/CA)” have been merged to the level of  “Rural and non (CMA/CA) or Prince Edward Island” .
```{r echo=F, include=F}
data <- gss %>% 
  select(age, sex, income_family, place_birth_canada, region, 
           education, pop_center, feelings_life, marital_status, 
           living_arrangement, self_rated_health, income_respondent,
           self_rated_mental_health, religion_has_affiliation,
           children_in_household, number_marriages)
data <- na.omit(data)
summary(data)
glimpse(data)
```

## Model

Introduce the selected model here. It is expected that you will use some mathematical notation here. If you do please ensure that all notation is explained. You may also want to discuss any special (hypothetical) cases of your model here, as well as any caveats.  



Our response variable is feelings of life, which is an ordinal variable ranging from 1 to 10.
(based on the summary of data information, we can see that the average feeling of life of the respondent is relatively high (mean=8.09). Despite the personal bias, our interest is what factors make people feel more satisfied about life than average level and what makes it equal or below average. Therefore, we create indicator variable ‘life_satisfication’, and it is labeled as high when respondents‘ feeling of life higher than average, otherise, labeled as ‘low’.

Since the response variable is an indicator, our final model is logistic model which use life satisfication as response variable and use gender, education level, living area, family income, marital status and self_rated_health as covariates. Hence, our model is 
\[
log(\frac{p}{1-p}) = \beta_0 +\beta_2x_1 +\beta_3x_2 +\beta_4x_3 +\beta_5x_4+\beta_6 x_5+\beta_7 x_6+ \epsilon
\]
where p represent the prebability to have life satisfaction below average. $x_i$(i=1,...,6) represent gender, education level, living area, family income, marital status and self_rated_health correspondingly, $\beta_i$(i=2,..,7) are estimate coefficient, $\beta_1$ is intercept, $\epsilon$ is random error.\par



```{r echo=F, include=F}
# reduce level of self_rated_health 
data$self_rated_health[data$self_rated_health[]=="Don't know"] <- "Fair"
data$self_rated_health[data$self_rated_health[]=="Very good"] <- "Good"
data$self_rated_health <- droplevels(data$self_rated_health)
# reduce level of education level
levels(data$education)[8:9] <- c("Bachelor or above",
                                  "college / below bachelor level")
data$education[data$education[]=="Bachelor's degree (e.g. B.A., B.Sc., LL.B.)"] <- "Bachelor or above"
data$education[data$education[]=="University certificate, diploma or degree above the bach..."] <- "Bachelor or above"
data$education[data$education[]=="University certificate or diploma below the bachelor's level"] <- "college / below bachelor level"
data$education[data$education[]=="College, CEGEP or other non-university certificate or di..."] <- "college / below bachelor level"
data$education[data$education[]=="Trade certificate or diploma"] <- "college / below bachelor level"
data$education <- droplevels(data$education)
# reduce level of living arrangement
levels(data$living_arrangement)[12:13] <- c("No spouse and children",
                                 "Spouse and children")

data$living_arrangement[data$living_arrangement[]=="No spouse and single child under 25 years of age" ]<-"No spouse and children"
data$living_arrangement[data$living_arrangement[]=="No spouse and single child 25 years of age or older" ]<-"No spouse and children"
data$living_arrangement[data$living_arrangement[]=="No spouse and non-single child(ren)" ]<-"No spouse and children"

data$living_arrangement[data$living_arrangement[]=="Spouse and single child under 25 years of age" ]<-"Spouse and children"
data$living_arrangement[data$living_arrangement[]=="Spouse and single child 25 years of age or older" ]<-"Spouse and children"
data$living_arrangement[data$living_arrangement[]=="Spouse and non-single child(ren)" ]<-"Spouse and children"
data$living_arrangement <- droplevels(data$living_arrangement)
# reduce level of pop_center
levels(data$pop_center)[4] <- c("Rural and non (CMA/CA) or Prince Edward Island")
data$pop_center[data$pop_center[]=="Prince Edward Island" ]<-"Rural and non (CMA/CA) or Prince Edward Island"
data$pop_center[data$pop_center[]=="Rural areas and small population centres (non CMA/CA)" ]<-"Rural and non (CMA/CA) or Prince Edward Island"
data$pop_center <- droplevels(data$pop_center)
# reduce level of income_family
levels(data$income_family)[7] <- "$50,000 to $124,999"
data$income_family[data$income_family[]=="$50,000 to $74,999"]<-"$50,000 to $124,999"
data$income_family[data$income_family[]=="$75,000 to $99,999"]<-"$50,000 to $124,999"
data$income_family[data$income_family[]=="$100,000 to $ 124,999"]<-"$50,000 to $124,999"
data$income_family <- droplevels(data$income_family)
```

```{r echo=F, include=F}
#for logistic model, divide feeling_of_life by mean
mean(data$feelings_life)
summary(as.factor(data$feelings_life))
data <- data %>% 
  mutate(life_satisfication = as.factor(ifelse(feelings_life>mean(feelings_life),'Higher','Lower')))
```

```{r ech=F, include=F}
#split data for validation
set.seed(304)
# 60% observations in train dataset, 40% in test data set
smp_size <- floor(0.6 * nrow(data))
train_ind <- sample(seq_len(nrow(data)), size = smp_size)
train <- data[train_ind, ]
test <- data[-train_ind, ]
```

```{r echo=F, include=F}
# fit logistic model
N=35151728
n=length(train$life_satisfication)
fpc.srs = rep(N, n)
train.srs <- svydesign(id=~1, data=train, fpc=fpc.srs)
train.logit <- svyglm(life_satisfication ~ sex + education + pop_center +
                       marital_status + self_rated_health +income_family, 
                       train.srs, family="binomial")
summary(train.logit) 
# use test dataset to test validity
N=35151728	
n=length(test$life_satisfication)
fpc.srs = rep(N, n)
test.srs <- svydesign(id=~1, data=test, fpc=fpc.srs)
test.logit <- svyglm(life_satisfication ~ sex + education + pop_center +
                       marital_status + self_rated_health + income_family, 
                       test.srs, family="binomial")
summary(test.logit)
```



## Results
```{r echo=F}
beta1 <- coef(train.logit)
beta2 <- coef(test.logit)
SD <-  summary(train.logit)$coef[,2]
p_value = format(summary(train.logit)$coef[,4], scientific = TRUE, digits = 4)
# table of coefficient
kable(cbind(round(exp(beta2),3), round(exp(beta1),3),
            round(exp(SD),3), p_value),
      col.names = c('test','train', 'SD','P value'),
      booktabs = TRUE,
      caption = "Summary of Model")
```
According to the summary of the final model, the odds of life satisfaction level below average will increase by a factor of 1.1 for male than female.

For the respondent’s education that is less than high school diploma or its equivalent, the odds of life satisfaction level below average will decrease by a factor of 0.724 compared to the Bachelor level.
The odds of life satisfaction level below average for the respondent’s education that is Bachelor or above will increase by 23.7% compared to the Bachelor.
According to the summary of the final model, the odds of life satisfaction level below average will increase by 4.4% for the respondent’s education that is college or below bachelor level than the Bachelor level.

The odds of life satisfaction level below average will decrease by a factor of 0.853 for the population center is Rural and non (CMA/CA) or Prince Edward Island compared to larger urban population centres (CMA/CA).

For the respondent’s marital status is living common-law, the odds of life satisfaction level below average will decrease by a factor of 0.729 compared to the divorced.
According to the summary, the odds of life satisfaction level below average will decrease by a factor of 0.507 for the married than the divorced.
The odds of life satisfaction level below average for separated respondents will increase by 46.2% compared to the divorced.
For the single, never-married respondent, the odds of life satisfaction level below average will increase by 17.7% compared to the divorced.
From the summary of the final model, it is found that the odds of life satisfaction level below average will decrease by a factor of 0.751 for the widowed compared to  the divorced.

For the respondent’s self-rated health is fair, the odds of life satisfaction level below average will increase by a factor of 6.15 compared to the excellent.
The odds of life satisfaction level below average for respondents that self-rated health is good will increase by 272.6% compared to the excellent.
According to the summary, the odds of life satisfaction level below average will increase by a factor of 10.251 for the self-rated health is poor compared to the excellent.


For the case of family income from $25000 to $49999, the odds of life satisfaction level below average will increase by 121.1% compared to the family income that is higher than $125000.
According to the summary of the final model, the odds of life satisfaction level below average will increase by a factor of 1.40 for family income less than $25000 compared to the family income that is higher than $125000.
The odds of life satisfaction level below average for family income from $50000 to $124999 will increase by 18.8% compared to the family income that is higher than $125000.



 and its p-value which is  >0.05 indicates that it is not significant in determining the admit.
and its p-value which is <=0.05 indicates that it is significant in determining the admit.
and its p-value which is <=0.01 indicates that it is very significant in determining the admit.
and its p-value which is <=0.001 indicates that it is highly significant in determining the admit.


```{r echo=F}
#ROC curve
roc_p <- predict(train.logit, type = "response")
roc_l <- roc(train$life_satisfication ~ roc_p)
## Setting levels: control = 0, case = 1
## Setting direction: controls < cases
## The True Positive Rate ##
TPR <- roc_l$sensitivities
## The False Positive Rate ##
FPR <- 1 - roc_l$specificities
roc <- data.frame(FPR,TPR)
#ROC curve
ggplot(roc, aes(FPR,TPR)) + 
  geom_line(size = 2, alpha = 0.7,col='red') +
  geom_segment(aes(x = 0, xend = 1, y = 0, yend = 1), linetype="dashed") +
  labs(title = "Figure2. ROC Curve",
       x = "False Positive Rate (1-Specificity)", 
       y = "True Positive Rate (Sensitivity)") +
  annotate("text", x = 0.75, y = 0.5, vjust = 0, 
           label = paste("AUC =",round(auc(roc_l),2)))
```
As shown in ROC plot(`Figure \@ref(fig:fig2)`), the predictive of final model is 0.69 which is considered acceptable.



## Discussion

Here you will discuss conclusions drawn from the results and comment on how it relates to the original goal of the study (which was specified in the Introduction).

# Weaknesses

Here we discuss weaknesses of the study, data, analysis, etc. You can also discuss areas for improvement.

# Next Steps

Here you discuss subsequent work to be done after this report. This can include next steps in terms of statistical analysis (perhaps there is a more efficient algorithm available, or perhaps there is a caveat in the data that would allow for some new technique). Future steps should also be specified in terms of the study setting (eg. including a follow-up survey on something, or a subsequent study that would complement the conclusions of your report).


## References

## Appendix

```{r echo = F,include=F}
tt <- gss %>% 
  select(age, sex, feelings_life, place_birth_canada,  
         vis_minority, citizenship_status, own_rent,income_family, 
         education, pop_center, marital_status, 
         living_arrangement, self_rated_health, 
         self_rated_mental_health, religion_has_affiliation,
         children_in_household, number_marriages)


table_one <- tableby(gss$region ~ ., data = tt)
summary(table_one, title = "Gapminder Data")
```



\begin{landscape}
\begin{longtable}[c]{lllllll}
\hline
\textbf{}                                                                                                                        & \textbf{\begin{tabular}[c]{@{}l@{}}Atlantic region \\ (N=4564)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}British Columbia\\  (N=2522)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Ontario\\  (N=5621)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Prairie region \\ (N=4073)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Quebec \\ (N=3822)\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Total \\ (N=20602)\end{tabular}} \\ \hline
\endfirsthead
%
\endhead
%
\multicolumn{1}{|l|}{Age}                                                                                                        & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{Mean (SD)}                                                                                                  & \multicolumn{1}{l|}{53.526 (17.244)}                                         & \multicolumn{1}{l|}{53.052 (17.868)}                                          & \multicolumn{1}{l|}{51.913 (17.822)}                                 & \multicolumn{1}{l|}{50.746 (18.059)}                                        & \multicolumn{1}{l|}{51.974 (17.681)}                                & \multicolumn{1}{l|}{52.190 (17.747)}                                \\ \hline
\multicolumn{1}{|l|}{Range}                                                                                                      & \multicolumn{1}{l|}{15.200 - 80.000}                                         & \multicolumn{1}{l|}{15.000 - 80.000}                                          & \multicolumn{1}{l|}{15.000 - 80.000}                                 & \multicolumn{1}{l|}{15.000 - 80.000}                                        & \multicolumn{1}{l|}{15.000 - 80.000}                                & \multicolumn{1}{l|}{15.000 - 80.000}                                \\ \hline
\multicolumn{1}{|l|}{Sex}                                                                                                        & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{Female}                                                                                                     & \multicolumn{1}{l|}{2537 (55.6\%)}                                           & \multicolumn{1}{l|}{1352 (53.6\%)}                                            & \multicolumn{1}{l|}{3082 (54.8\%)}                                   & \multicolumn{1}{l|}{2157 (53.0\%)}                                          & \multicolumn{1}{l|}{2075 (54.3\%)}                                  & \multicolumn{1}{l|}{11203 (54.4\%)}                                 \\ \hline
\multicolumn{1}{|l|}{Male}                                                                                                       & \multicolumn{1}{l|}{2027 (44.4\%)}                                           & \multicolumn{1}{l|}{1170 (46.4\%)}                                            & \multicolumn{1}{l|}{2539 (45.2\%)}                                   & \multicolumn{1}{l|}{1916 (47.0\%)}                                          & \multicolumn{1}{l|}{1747 (45.7\%)}                                  & \multicolumn{1}{l|}{9399 (45.6\%)}                                  \\ \hline
\multicolumn{1}{|l|}{feelings\_life}                                                                                             & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{N-Miss}                                                                                                     & \multicolumn{1}{l|}{67}                                                      & \multicolumn{1}{l|}{30}                                                       & \multicolumn{1}{l|}{85}                                              & \multicolumn{1}{l|}{53}                                                     & \multicolumn{1}{l|}{36}                                             & \multicolumn{1}{l|}{271}                                            \\ \hline
\multicolumn{1}{|l|}{Mean (SD)}                                                                                                  & \multicolumn{1}{l|}{8.161 (1.635)}                                           & \multicolumn{1}{l|}{8.023 (1.684)}                                            & \multicolumn{1}{l|}{8.064 (1.696)}                                   & \multicolumn{1}{l|}{8.101 (1.678)}                                          & \multicolumn{1}{l|}{8.101 (1.514)}                                  & \multicolumn{1}{l|}{8.094 (1.645)}                                  \\ \hline
\multicolumn{1}{|l|}{Range}                                                                                                      & \multicolumn{1}{l|}{0.000 - 10.000}                                          & \multicolumn{1}{l|}{0.000 - 10.000}                                           & \multicolumn{1}{l|}{0.000 - 10.000}                                  & \multicolumn{1}{l|}{0.000 - 10.000}                                         & \multicolumn{1}{l|}{0.000 - 10.000}                                 & \multicolumn{1}{l|}{0.000 - 10.000}                                 \\ \hline
\multicolumn{1}{|l|}{place\_birth\_canada}                                                                                       & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{N-Miss}                                                                                                     & \multicolumn{1}{l|}{18}                                                      & \multicolumn{1}{l|}{13}                                                       & \multicolumn{1}{l|}{29}                                              & \multicolumn{1}{l|}{24}                                                     & \multicolumn{1}{l|}{13}                                             & \multicolumn{1}{l|}{97}                                             \\ \hline
\multicolumn{1}{|l|}{Born in Canada}                                                                                             & \multicolumn{1}{l|}{4237 (93.2\%)}                                           & \multicolumn{1}{l|}{1757 (70.0\%)}                                            & \multicolumn{1}{l|}{3806 (68.1\%)}                                   & \multicolumn{1}{l|}{3300 (81.5\%)}                                          & \multicolumn{1}{l|}{3255 (85.5\%)}                                  & \multicolumn{1}{l|}{16355 (79.8\%)}                                 \\ \hline
\multicolumn{1}{|l|}{Born outside Canada}                                                                                        & \multicolumn{1}{l|}{277 (6.1\%)}                                             & \multicolumn{1}{l|}{752 (30.0\%)}                                             & \multicolumn{1}{l|}{1780 (31.8\%)}                                   & \multicolumn{1}{l|}{738 (18.2\%)}                                           & \multicolumn{1}{l|}{550 (14.4\%)}                                   & \multicolumn{1}{l|}{4097 (20.0\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Don’t know}                                                                                                 & \multicolumn{1}{l|}{32 (0.7\%)}                                              & \multicolumn{1}{l|}{0 (0.0\%)}                                                & \multicolumn{1}{l|}{6 (0.1\%)}                                       & \multicolumn{1}{l|}{11 (0.3\%)}                                             & \multicolumn{1}{l|}{4 (0.1\%)}                                      & \multicolumn{1}{l|}{53 (0.3\%)}                                     \\ \hline
\multicolumn{1}{|l|}{vis\_minority}                                                                                              & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{N-Miss}                                                                                                     & \multicolumn{1}{l|}{25}                                                      & \multicolumn{1}{l|}{23}                                                       & \multicolumn{1}{l|}{43}                                              & \multicolumn{1}{l|}{33}                                                     & \multicolumn{1}{l|}{16}                                             & \multicolumn{1}{l|}{140}                                            \\ \hline
\multicolumn{1}{|l|}{Don’t know}                                                                                                 & \multicolumn{1}{l|}{53 (1.2\%)}                                              & \multicolumn{1}{l|}{32 (1.3\%)}                                               & \multicolumn{1}{l|}{123 (2.2\%)}                                     & \multicolumn{1}{l|}{67 (1.7\%)}                                             & \multicolumn{1}{l|}{39 (1.0\%)}                                     & \multicolumn{1}{l|}{314 (1.5\%)}                                    \\ \hline
\multicolumn{1}{|l|}{Not a visible minority}                                                                                     & \multicolumn{1}{l|}{4376 (96.4\%)}                                           & \multicolumn{1}{l|}{1994 (79.8\%)}                                            & \multicolumn{1}{l|}{4265 (76.5\%)}                                   & \multicolumn{1}{l|}{3504 (86.7\%)}                                          & \multicolumn{1}{l|}{3435 (90.3\%)}                                  & \multicolumn{1}{l|}{17574 (85.9\%)}                                 \\ \hline
\multicolumn{1}{|l|}{Visible minority}                                                                                           & \multicolumn{1}{l|}{110 (2.4\%)}                                             & \multicolumn{1}{l|}{473 (18.9\%)}                                             & \multicolumn{1}{l|}{1190 (21.3\%)}                                   & \multicolumn{1}{l|}{469 (11.6\%)}                                           & \multicolumn{1}{l|}{332 (8.7\%)}                                    & \multicolumn{1}{l|}{2574 (12.6\%)}                                  \\ \hline
\multicolumn{1}{|l|}{citizenship\_status}                                                                                        & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{N-Miss}                                                                                                     & \multicolumn{1}{l|}{114}                                                     & \multicolumn{1}{l|}{202}                                                      & \multicolumn{1}{l|}{356}                                             & \multicolumn{1}{l|}{294}                                                    & \multicolumn{1}{l|}{177}                                            & \multicolumn{1}{l|}{1143}                                           \\ \hline
\multicolumn{1}{|l|}{By birth}                                                                                                   & \multicolumn{1}{l|}{4252 (95.6\%)}                                           & \multicolumn{1}{l|}{1779 (76.7\%)}                                            & \multicolumn{1}{l|}{3826 (72.7\%)}                                   & \multicolumn{1}{l|}{3318 (87.8\%)}                                          & \multicolumn{1}{l|}{3264 (89.5\%)}                                  & \multicolumn{1}{l|}{16439 (84.5\%)}                                 \\ \hline
\multicolumn{1}{|l|}{By naturalization}                                                                                          & \multicolumn{1}{l|}{166 (3.7\%)}                                             & \multicolumn{1}{l|}{539 (23.2\%)}                                             & \multicolumn{1}{l|}{1429 (27.1\%)}                                   & \multicolumn{1}{l|}{453 (12.0\%)}                                           & \multicolumn{1}{l|}{377 (10.3\%)}                                   & \multicolumn{1}{l|}{2964 (15.2\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Don’t know}                                                                                                 & \multicolumn{1}{l|}{32 (0.7\%)}                                              & \multicolumn{1}{l|}{2 (0.1\%)}                                                & \multicolumn{1}{l|}{10 (0.2\%)}                                      & \multicolumn{1}{l|}{8 (0.2\%)}                                              & \multicolumn{1}{l|}{4 (0.1\%)}                                      & \multicolumn{1}{l|}{56 (0.3\%)}                                     \\ \hline
\multicolumn{1}{|l|}{own\_rent}                                                                                                  & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{N-Miss}                                                                                                     & \multicolumn{1}{l|}{27}                                                      & \multicolumn{1}{l|}{18}                                                       & \multicolumn{1}{l|}{33}                                              & \multicolumn{1}{l|}{29}                                                     & \multicolumn{1}{l|}{13}                                             & \multicolumn{1}{l|}{120}                                            \\ \hline
\multicolumn{1}{|l|}{Don’t know}                                                                                                 & \multicolumn{1}{l|}{27 (0.6\%)}                                              & \multicolumn{1}{l|}{16 (0.6\%)}                                               & \multicolumn{1}{l|}{15 (0.3\%)}                                      & \multicolumn{1}{l|}{11 (0.3\%)}                                             & \multicolumn{1}{l|}{2 (0.1\%)}                                      & \multicolumn{1}{l|}{71 (0.3\%)}                                     \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}Owned by you or a member \\ of this household…\end{tabular}}                     & \multicolumn{1}{l|}{3467 (76.4\%)}                                           & \multicolumn{1}{l|}{1817 (72.6\%)}                                            & \multicolumn{1}{l|}{4168 (74.6\%)}                                   & \multicolumn{1}{l|}{3162 (78.2\%)}                                          & \multicolumn{1}{l|}{2480 (65.1\%)}                                  & \multicolumn{1}{l|}{15094 (73.7\%)}                                 \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}Rented, even if no \\ cash rent is paid\end{tabular}}                            & \multicolumn{1}{l|}{1043 (23.0\%)}                                           & \multicolumn{1}{l|}{671 (26.8\%)}                                             & \multicolumn{1}{l|}{1405 (25.1\%)}                                   & \multicolumn{1}{l|}{871 (21.5\%)}                                           & \multicolumn{1}{l|}{1327 (34.8\%)}                                  & \multicolumn{1}{l|}{5317 (26.0\%)}                                  \\ \hline
\multicolumn{1}{|l|}{income\_family}                                                                                             & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{$100,000 to $ 124,999}                                                                                      & \multicolumn{1}{l|}{434 (9.5\%)}                                             & \multicolumn{1}{l|}{267 (10.6\%)}                                             & \multicolumn{1}{l|}{634 (11.3\%)}                                    & \multicolumn{1}{l|}{464 (11.4\%)}                                           & \multicolumn{1}{l|}{359 (9.4\%)}                                    & \multicolumn{1}{l|}{2158 (10.5\%)}                                  \\ \hline
\multicolumn{1}{|l|}{\$125,000 and more}                                                                                         & \multicolumn{1}{l|}{898 (19.7\%)}                                            & \multicolumn{1}{l|}{608 (24.1\%)}                                             & \multicolumn{1}{l|}{1510 (26.9\%)}                                   & \multicolumn{1}{l|}{1036 (25.4\%)}                                          & \multicolumn{1}{l|}{655 (17.1\%)}                                   & \multicolumn{1}{l|}{4707 (22.8\%)}                                  \\ \hline
\multicolumn{1}{|l|}{$25,000 to $49,999}                                                                                         & \multicolumn{1}{l|}{1050 (23.0\%)}                                           & \multicolumn{1}{l|}{515 (20.4\%)}                                             & \multicolumn{1}{l|}{1024 (18.2\%)}                                   & \multicolumn{1}{l|}{821 (20.2\%)}                                           & \multicolumn{1}{l|}{935 (24.5\%)}                                   & \multicolumn{1}{l|}{4345 (21.1\%)}                                  \\ \hline
\multicolumn{1}{|l|}{$50,000 to $74,999}                                                                                         & \multicolumn{1}{l|}{844 (18.5\%)}                                            & \multicolumn{1}{l|}{419 (16.6\%)}                                             & \multicolumn{1}{l|}{993 (17.7\%)}                                    & \multicolumn{1}{l|}{715 (17.6\%)}                                           & \multicolumn{1}{l|}{725 (19.0\%)}                                   & \multicolumn{1}{l|}{3696 (17.9\%)}                                  \\ \hline
\multicolumn{1}{|l|}{$75,000 to $99,999}                                                                                         & \multicolumn{1}{l|}{679 (14.9\%)}                                            & \multicolumn{1}{l|}{366 (14.5\%)}                                             & \multicolumn{1}{l|}{778 (13.8\%)}                                    & \multicolumn{1}{l|}{559 (13.7\%)}                                           & \multicolumn{1}{l|}{539 (14.1\%)}                                   & \multicolumn{1}{l|}{2921 (14.2\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Less than \$25,000}                                                                                         & \multicolumn{1}{l|}{659 (14.4\%)}                                            & \multicolumn{1}{l|}{347 (13.8\%)}                                             & \multicolumn{1}{l|}{682 (12.1\%)}                                    & \multicolumn{1}{l|}{478 (11.7\%)}                                           & \multicolumn{1}{l|}{609 (15.9\%)}                                   & \multicolumn{1}{l|}{2775 (13.5\%)}                                  \\ \hline
\multicolumn{1}{|l|}{education}                                                                                                  & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{N-Miss}                                                                                                     & \multicolumn{1}{l|}{71}                                                      & \multicolumn{1}{l|}{42}                                                       & \multicolumn{1}{l|}{90}                                              & \multicolumn{1}{l|}{80}                                                     & \multicolumn{1}{l|}{58}                                             & \multicolumn{1}{l|}{341}                                            \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}Bachelor’s degree \\ (e.g. B.A., B.Sc., LL.B.)\end{tabular}}                     & \multicolumn{1}{l|}{717 (16.0\%)}                                            & \multicolumn{1}{l|}{520 (21.0\%)}                                             & \multicolumn{1}{l|}{1179 (21.3\%)}                                   & \multicolumn{1}{l|}{687 (17.2\%)}                                           & \multicolumn{1}{l|}{650 (17.3\%)}                                   & \multicolumn{1}{l|}{3753 (18.5\%)}                                  \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}College, CEGEP \\ or other non-university\\  certificate or di…\end{tabular}}    & \multicolumn{1}{l|}{1068 (23.8\%)}                                           & \multicolumn{1}{l|}{519 (20.9\%)}                                             & \multicolumn{1}{l|}{1388 (25.1\%)}                                   & \multicolumn{1}{l|}{836 (20.9\%)}                                           & \multicolumn{1}{l|}{755 (20.1\%)}                                   & \multicolumn{1}{l|}{4566 (22.5\%)}                                  \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}High school diploma or \\ a high school \\ equivalency certificate\end{tabular}} & \multicolumn{1}{l|}{1065 (23.7\%)}                                           & \multicolumn{1}{l|}{620 (25.0\%)}                                             & \multicolumn{1}{l|}{1302 (23.5\%)}                                   & \multicolumn{1}{l|}{1082 (27.1\%)}                                          & \multicolumn{1}{l|}{779 (20.7\%)}                                   & \multicolumn{1}{l|}{4848 (23.9\%)}                                  \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}Less than high school \\ diploma or its equivalent\end{tabular}}                 & \multicolumn{1}{l|}{804 (17.9\%)}                                            & \multicolumn{1}{l|}{269 (10.8\%)}                                             & \multicolumn{1}{l|}{660 (11.9\%)}                                    & \multicolumn{1}{l|}{582 (14.6\%)}                                           & \multicolumn{1}{l|}{721 (19.2\%)}                                   & \multicolumn{1}{l|}{3036 (15.0\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Trade certificate or diploma}                                                                               & \multicolumn{1}{l|}{354 (7.9\%)}                                             & \multicolumn{1}{l|}{173 (7.0\%)}                                              & \multicolumn{1}{l|}{184 (3.3\%)}                                     & \multicolumn{1}{l|}{356 (8.9\%)}                                            & \multicolumn{1}{l|}{416 (11.1\%)}                                   & \multicolumn{1}{l|}{1483 (7.3\%)}                                   \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}University certificate or \\ diploma below the \\ bachelor’s level\end{tabular}} & \multicolumn{1}{l|}{135 (3.0\%)}                                             & \multicolumn{1}{l|}{122 (4.9\%)}                                              & \multicolumn{1}{l|}{158 (2.9\%)}                                     & \multicolumn{1}{l|}{178 (4.5\%)}                                            & \multicolumn{1}{l|}{139 (3.7\%)}                                    & \multicolumn{1}{l|}{732 (3.6\%)}                                    \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}University certificate, \\ diploma or degree \\ above the bach…\end{tabular}}    & \multicolumn{1}{l|}{350 (7.8\%)}                                             & \multicolumn{1}{l|}{257 (10.4\%)}                                             & \multicolumn{1}{l|}{660 (11.9\%)}                                    & \multicolumn{1}{l|}{272 (6.8\%)}                                            & \multicolumn{1}{l|}{304 (8.1\%)}                                    & \multicolumn{1}{l|}{1843 (9.1\%)}                                   \\ \hline
\multicolumn{1}{|l|}{pop\_center}                                                                                                & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}Larger urban population \\ centres (CMA/CA)\end{tabular}}                        & \multicolumn{1}{l|}{2592 (56.8\%)}                                           & \multicolumn{1}{l|}{2246 (89.1\%)}                                            & \multicolumn{1}{l|}{5067 (90.1\%)}                                   & \multicolumn{1}{l|}{2898 (71.2\%)}                                          & \multicolumn{1}{l|}{3124 (81.7\%)}                                  & \multicolumn{1}{l|}{15927 (77.3\%)}                                 \\ \hline
\multicolumn{1}{|l|}{Prince Edward Island}                                                                                       & \multicolumn{1}{l|}{708 (15.5\%)}                                            & \multicolumn{1}{l|}{0 (0.0\%)}                                                & \multicolumn{1}{l|}{0 (0.0\%)}                                       & \multicolumn{1}{l|}{0 (0.0\%)}                                              & \multicolumn{1}{l|}{0 (0.0\%)}                                      & \multicolumn{1}{l|}{708 (3.4\%)}                                    \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}Rural areas and small \\ population centres\\  (non CMA/CA)\end{tabular}}        & \multicolumn{1}{l|}{1264 (27.7\%)}                                           & \multicolumn{1}{l|}{276 (10.9\%)}                                             & \multicolumn{1}{l|}{554 (9.9\%)}                                     & \multicolumn{1}{l|}{1175 (28.8\%)}                                          & \multicolumn{1}{l|}{698 (18.3\%)}                                   & \multicolumn{1}{l|}{3967 (19.3\%)}                                  \\ \hline
\multicolumn{1}{|l|}{marital\_status}                                                                                            & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{N-Miss}                                                                                                     & \multicolumn{1}{l|}{1}                                                       & \multicolumn{1}{l|}{0}                                                        & \multicolumn{1}{l|}{1}                                               & \multicolumn{1}{l|}{4}                                                      & \multicolumn{1}{l|}{1}                                              & \multicolumn{1}{l|}{7}                                              \\ \hline
\multicolumn{1}{|l|}{Divorced}                                                                                                   & \multicolumn{1}{l|}{350 (7.7\%)}                                             & \multicolumn{1}{l|}{228 (9.0\%)}                                              & \multicolumn{1}{l|}{478 (8.5\%)}                                     & \multicolumn{1}{l|}{333 (8.2\%)}                                            & \multicolumn{1}{l|}{378 (9.9\%)}                                    & \multicolumn{1}{l|}{1767 (8.6\%)}                                   \\ \hline
\multicolumn{1}{|l|}{Living common-law}                                                                                          & \multicolumn{1}{l|}{443 (9.7\%)}                                             & \multicolumn{1}{l|}{195 (7.7\%)}                                              & \multicolumn{1}{l|}{381 (6.8\%)}                                     & \multicolumn{1}{l|}{258 (6.3\%)}                                            & \multicolumn{1}{l|}{798 (20.9\%)}                                   & \multicolumn{1}{l|}{2075 (10.1\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Married}                                                                                                    & \multicolumn{1}{l|}{2185 (47.9\%)}                                           & \multicolumn{1}{l|}{1243 (49.3\%)}                                            & \multicolumn{1}{l|}{2708 (48.2\%)}                                   & \multicolumn{1}{l|}{2125 (52.2\%)}                                          & \multicolumn{1}{l|}{1240 (32.5\%)}                                  & \multicolumn{1}{l|}{9501 (46.1\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Separated}                                                                                                  & \multicolumn{1}{l|}{183 (4.0\%)}                                             & \multicolumn{1}{l|}{79 (3.1\%)}                                               & \multicolumn{1}{l|}{206 (3.7\%)}                                     & \multicolumn{1}{l|}{95 (2.3\%)}                                             & \multicolumn{1}{l|}{80 (2.1\%)}                                     & \multicolumn{1}{l|}{643 (3.1\%)}                                    \\ \hline
\multicolumn{1}{|l|}{Single, never married}                                                                                      & \multicolumn{1}{l|}{903 (19.8\%)}                                            & \multicolumn{1}{l|}{562 (22.3\%)}                                             & \multicolumn{1}{l|}{1328 (23.6\%)}                                   & \multicolumn{1}{l|}{888 (21.8\%)}                                           & \multicolumn{1}{l|}{1029 (26.9\%)}                                  & \multicolumn{1}{l|}{4710 (22.9\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Widowed}                                                                                                    & \multicolumn{1}{l|}{499 (10.9\%)}                                            & \multicolumn{1}{l|}{215 (8.5\%)}                                              & \multicolumn{1}{l|}{519 (9.2\%)}                                     & \multicolumn{1}{l|}{370 (9.1\%)}                                            & \multicolumn{1}{l|}{296 (7.7\%)}                                    & \multicolumn{1}{l|}{1899 (9.2\%)}                                   \\ \hline
\multicolumn{1}{|l|}{living\_arrangement}                                                                                        & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{Alone}                                                                                                      & \multicolumn{1}{l|}{1247 (27.3\%)}                                           & \multicolumn{1}{l|}{747 (29.6\%)}                                             & \multicolumn{1}{l|}{1544 (27.5\%)}                                   & \multicolumn{1}{l|}{1097 (26.9\%)}                                          & \multicolumn{1}{l|}{1180 (30.9\%)}                                  & \multicolumn{1}{l|}{5815 (28.2\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Living with one parent}                                                                                     & \multicolumn{1}{l|}{109 (2.4\%)}                                             & \multicolumn{1}{l|}{49 (1.9\%)}                                               & \multicolumn{1}{l|}{160 (2.8\%)}                                     & \multicolumn{1}{l|}{81 (2.0\%)}                                             & \multicolumn{1}{l|}{112 (2.9\%)}                                    & \multicolumn{1}{l|}{511 (2.5\%)}                                    \\ \hline
\multicolumn{1}{|l|}{Living with two parents}                                                                                    & \multicolumn{1}{l|}{167 (3.7\%)}                                             & \multicolumn{1}{l|}{121 (4.8\%)}                                              & \multicolumn{1}{l|}{337 (6.0\%)}                                     & \multicolumn{1}{l|}{188 (4.6\%)}                                            & \multicolumn{1}{l|}{159 (4.2\%)}                                    & \multicolumn{1}{l|}{972 (4.7\%)}                                    \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}No spouse and \\ non-single child(ren)\end{tabular}}                             & \multicolumn{1}{l|}{1 (0.0\%)}                                               & \multicolumn{1}{l|}{2 (0.1\%)}                                                & \multicolumn{1}{l|}{9 (0.2\%)}                                       & \multicolumn{1}{l|}{5 (0.1\%)}                                              & \multicolumn{1}{l|}{3 (0.1\%)}                                      & \multicolumn{1}{l|}{20 (0.1\%)}                                     \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}No spouse and single \\ child 25 years of age\\  or older\end{tabular}}          & \multicolumn{1}{l|}{41 (0.9\%)}                                              & \multicolumn{1}{l|}{22 (0.9\%)}                                               & \multicolumn{1}{l|}{78 (1.4\%)}                                      & \multicolumn{1}{l|}{41 (1.0\%)}                                             & \multicolumn{1}{l|}{31 (0.8\%)}                                     & \multicolumn{1}{l|}{213 (1.0\%)}                                    \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}No spouse and single \\ child under 25 years of age\end{tabular}}                & \multicolumn{1}{l|}{190 (4.2\%)}                                             & \multicolumn{1}{l|}{70 (2.8\%)}                                               & \multicolumn{1}{l|}{238 (4.2\%)}                                     & \multicolumn{1}{l|}{130 (3.2\%)}                                            & \multicolumn{1}{l|}{186 (4.9\%)}                                    & \multicolumn{1}{l|}{814 (4.0\%)}                                    \\ \hline
\multicolumn{1}{|l|}{Other living arrangement}                                                                                   & \multicolumn{1}{l|}{254 (5.6\%)}                                             & \multicolumn{1}{l|}{153 (6.1\%)}                                              & \multicolumn{1}{l|}{292 (5.2\%)}                                     & \multicolumn{1}{l|}{269 (6.6\%)}                                            & \multicolumn{1}{l|}{166 (4.3\%)}                                    & \multicolumn{1}{l|}{1134 (5.5\%)}                                   \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}Spouse and non-single\\  child(ren)\end{tabular}}                                & \multicolumn{1}{l|}{1 (0.0\%)}                                               & \multicolumn{1}{l|}{1 (0.0\%)}                                                & \multicolumn{1}{l|}{7 (0.1\%)}                                       & \multicolumn{1}{l|}{2 (0.0\%)}                                              & \multicolumn{1}{l|}{0 (0.0\%)}                                      & \multicolumn{1}{l|}{11 (0.1\%)}                                     \\ \hline
\multicolumn{1}{|l|}{Spouse and other}                                                                                           & \multicolumn{1}{l|}{46 (1.0\%)}                                              & \multicolumn{1}{l|}{21 (0.8\%)}                                               & \multicolumn{1}{l|}{69 (1.2\%)}                                      & \multicolumn{1}{l|}{44 (1.1\%)}                                             & \multicolumn{1}{l|}{25 (0.7\%)}                                     & \multicolumn{1}{l|}{205 (1.0\%)}                                    \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}Spouse and single child 25 \\ years of age or older\end{tabular}}                & \multicolumn{1}{l|}{91 (2.0\%)}                                              & \multicolumn{1}{l|}{40 (1.6\%)}                                               & \multicolumn{1}{l|}{137 (2.4\%)}                                     & \multicolumn{1}{l|}{61 (1.5\%)}                                             & \multicolumn{1}{l|}{44 (1.2\%)}                                     & \multicolumn{1}{l|}{373 (1.8\%)}                                    \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}Spouse and single child \\ under 25 years of age\end{tabular}}                   & \multicolumn{1}{l|}{799 (17.5\%)}                                            & \multicolumn{1}{l|}{482 (19.1\%)}                                             & \multicolumn{1}{l|}{1191 (21.2\%)}                                   & \multicolumn{1}{l|}{890 (21.9\%)}                                           & \multicolumn{1}{l|}{774 (20.3\%)}                                   & \multicolumn{1}{l|}{4136 (20.1\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Spouse only}                                                                                                & \multicolumn{1}{l|}{1618 (35.5\%)}                                           & \multicolumn{1}{l|}{814 (32.3\%)}                                             & \multicolumn{1}{l|}{1559 (27.7\%)}                                   & \multicolumn{1}{l|}{1265 (31.1\%)}                                          & \multicolumn{1}{l|}{1142 (29.9\%)}                                  & \multicolumn{1}{l|}{6398 (31.1\%)}                                  \\ \hline
\multicolumn{1}{|l|}{self\_rated\_health}                                                                                        & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{N-Miss}                                                                                                     & \multicolumn{1}{l|}{19}                                                      & \multicolumn{1}{l|}{16}                                                       & \multicolumn{1}{l|}{33}                                              & \multicolumn{1}{l|}{19}                                                     & \multicolumn{1}{l|}{12}                                             & \multicolumn{1}{l|}{99}                                             \\ \hline
\multicolumn{1}{|l|}{Don’t know}                                                                                                 & \multicolumn{1}{l|}{18 (0.4\%)}                                              & \multicolumn{1}{l|}{6 (0.2\%)}                                                & \multicolumn{1}{l|}{18 (0.3\%)}                                      & \multicolumn{1}{l|}{10 (0.2\%)}                                             & \multicolumn{1}{l|}{5 (0.1\%)}                                      & \multicolumn{1}{l|}{57 (0.3\%)}                                     \\ \hline
\multicolumn{1}{|l|}{Excellent}                                                                                                  & \multicolumn{1}{l|}{833 (18.3\%)}                                            & \multicolumn{1}{l|}{566 (22.6\%)}                                             & \multicolumn{1}{l|}{1206 (21.6\%)}                                   & \multicolumn{1}{l|}{839 (20.7\%)}                                           & \multicolumn{1}{l|}{932 (24.5\%)}                                   & \multicolumn{1}{l|}{4376 (21.3\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Fair}                                                                                                       & \multicolumn{1}{l|}{542 (11.9\%)}                                            & \multicolumn{1}{l|}{248 (9.9\%)}                                              & \multicolumn{1}{l|}{517 (9.3\%)}                                     & \multicolumn{1}{l|}{426 (10.5\%)}                                           & \multicolumn{1}{l|}{345 (9.1\%)}                                    & \multicolumn{1}{l|}{2078 (10.1\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Good}                                                                                                       & \multicolumn{1}{l|}{1303 (28.7\%)}                                           & \multicolumn{1}{l|}{771 (30.8\%)}                                             & \multicolumn{1}{l|}{1676 (30.0\%)}                                   & \multicolumn{1}{l|}{1250 (30.8\%)}                                          & \multicolumn{1}{l|}{1162 (30.5\%)}                                  & \multicolumn{1}{l|}{6162 (30.1\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Poor}                                                                                                       & \multicolumn{1}{l|}{216 (4.8\%)}                                             & \multicolumn{1}{l|}{116 (4.6\%)}                                              & \multicolumn{1}{l|}{234 (4.2\%)}                                     & \multicolumn{1}{l|}{155 (3.8\%)}                                            & \multicolumn{1}{l|}{95 (2.5\%)}                                     & \multicolumn{1}{l|}{816 (4.0\%)}                                    \\ \hline
\multicolumn{1}{|l|}{Very good}                                                                                                  & \multicolumn{1}{l|}{1633 (35.9\%)}                                           & \multicolumn{1}{l|}{799 (31.9\%)}                                             & \multicolumn{1}{l|}{1937 (34.7\%)}                                   & \multicolumn{1}{l|}{1374 (33.9\%)}                                          & \multicolumn{1}{l|}{1271 (33.4\%)}                                  & \multicolumn{1}{l|}{7014 (34.2\%)}                                  \\ \hline
\multicolumn{1}{|l|}{self\_rated\_mental\_health}                                                                                & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{N-Miss}                                                                                                     & \multicolumn{1}{l|}{19}                                                      & \multicolumn{1}{l|}{19}                                                       & \multicolumn{1}{l|}{34}                                              & \multicolumn{1}{l|}{22}                                                     & \multicolumn{1}{l|}{12}                                             & \multicolumn{1}{l|}{106}                                            \\ \hline
\multicolumn{1}{|l|}{Don’t know}                                                                                                 & \multicolumn{1}{l|}{16 (0.4\%)}                                              & \multicolumn{1}{l|}{4 (0.2\%)}                                                & \multicolumn{1}{l|}{16 (0.3\%)}                                      & \multicolumn{1}{l|}{9 (0.2\%)}                                              & \multicolumn{1}{l|}{12 (0.3\%)}                                     & \multicolumn{1}{l|}{57 (0.3\%)}                                     \\ \hline
\multicolumn{1}{|l|}{Excellent}                                                                                                  & \multicolumn{1}{l|}{1156 (25.4\%)}                                           & \multicolumn{1}{l|}{714 (28.5\%)}                                             & \multicolumn{1}{l|}{1726 (30.9\%)}                                   & \multicolumn{1}{l|}{1134 (28.0\%)}                                          & \multicolumn{1}{l|}{1350 (35.4\%)}                                  & \multicolumn{1}{l|}{6080 (29.7\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Fair}                                                                                                       & \multicolumn{1}{l|}{340 (7.5\%)}                                             & \multicolumn{1}{l|}{174 (7.0\%)}                                              & \multicolumn{1}{l|}{361 (6.5\%)}                                     & \multicolumn{1}{l|}{261 (6.4\%)}                                            & \multicolumn{1}{l|}{160 (4.2\%)}                                    & \multicolumn{1}{l|}{1296 (6.3\%)}                                   \\ \hline
\multicolumn{1}{|l|}{Good}                                                                                                       & \multicolumn{1}{l|}{1385 (30.5\%)}                                           & \multicolumn{1}{l|}{730 (29.2\%)}                                             & \multicolumn{1}{l|}{1504 (26.9\%)}                                   & \multicolumn{1}{l|}{1196 (29.5\%)}                                          & \multicolumn{1}{l|}{998 (26.2\%)}                                   & \multicolumn{1}{l|}{5813 (28.4\%)}                                  \\ \hline
\multicolumn{1}{|l|}{Poor}                                                                                                       & \multicolumn{1}{l|}{79 (1.7\%)}                                              & \multicolumn{1}{l|}{54 (2.2\%)}                                               & \multicolumn{1}{l|}{99 (1.8\%)}                                      & \multicolumn{1}{l|}{70 (1.7\%)}                                             & \multicolumn{1}{l|}{24 (0.6\%)}                                     & \multicolumn{1}{l|}{326 (1.6\%)}                                    \\ \hline
\multicolumn{1}{|l|}{Very good}                                                                                                  & \multicolumn{1}{l|}{1569 (34.5\%)}                                           & \multicolumn{1}{l|}{827 (33.0\%)}                                             & \multicolumn{1}{l|}{1881 (33.7\%)}                                   & \multicolumn{1}{l|}{1381 (34.1\%)}                                          & \multicolumn{1}{l|}{1266 (33.2\%)}                                  & \multicolumn{1}{l|}{6924 (33.8\%)}                                  \\ \hline
\multicolumn{1}{|l|}{religion\_has\_affiliation}                                                                                 & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{N-Miss}                                                                                                     & \multicolumn{1}{l|}{48}                                                      & \multicolumn{1}{l|}{52}                                                       & \multicolumn{1}{l|}{84}                                              & \multicolumn{1}{l|}{71}                                                     & \multicolumn{1}{l|}{27}                                             & \multicolumn{1}{l|}{282}                                            \\ \hline
\multicolumn{1}{|l|}{Don’t know}                                                                                                 & \multicolumn{1}{l|}{39 (0.9\%)}                                              & \multicolumn{1}{l|}{35 (1.4\%)}                                               & \multicolumn{1}{l|}{32 (0.6\%)}                                      & \multicolumn{1}{l|}{42 (1.0\%)}                                             & \multicolumn{1}{l|}{11 (0.3\%)}                                     & \multicolumn{1}{l|}{159 (0.8\%)}                                    \\ \hline
\multicolumn{1}{|l|}{Has religious affiliation}                                                                                  & \multicolumn{1}{l|}{3840 (85.0\%)}                                           & \multicolumn{1}{l|}{1494 (60.5\%)}                                            & \multicolumn{1}{l|}{4386 (79.2\%)}                                   & \multicolumn{1}{l|}{3049 (76.2\%)}                                          & \multicolumn{1}{l|}{3386 (89.2\%)}                                  & \multicolumn{1}{l|}{16155 (79.5\%)}                                 \\ \hline
\multicolumn{1}{|l|}{No religious affiliation}                                                                                   & \multicolumn{1}{l|}{637 (14.1\%)}                                            & \multicolumn{1}{l|}{941 (38.1\%)}                                             & \multicolumn{1}{l|}{1119 (20.2\%)}                                   & \multicolumn{1}{l|}{911 (22.8\%)}                                           & \multicolumn{1}{l|}{398 (10.5\%)}                                   & \multicolumn{1}{l|}{4006 (19.7\%)}                                  \\ \hline
\multicolumn{1}{|l|}{children\_in\_household}                                                                                    & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{No child}                                                                                                   & \multicolumn{1}{l|}{3678 (80.6\%)}                                           & \multicolumn{1}{l|}{2015 (79.9\%)}                                            & \multicolumn{1}{l|}{4323 (76.9\%)}                                   & \multicolumn{1}{l|}{3039 (74.6\%)}                                          & \multicolumn{1}{l|}{2942 (77.0\%)}                                  & \multicolumn{1}{l|}{15997 (77.6\%)}                                 \\ \hline
\multicolumn{1}{|l|}{One child}                                                                                                  & \multicolumn{1}{l|}{433 (9.5\%)}                                             & \multicolumn{1}{l|}{236 (9.4\%)}                                              & \multicolumn{1}{l|}{577 (10.3\%)}                                    & \multicolumn{1}{l|}{421 (10.3\%)}                                           & \multicolumn{1}{l|}{378 (9.9\%)}                                    & \multicolumn{1}{l|}{2045 (9.9\%)}                                   \\ \hline
\multicolumn{1}{|l|}{Three or more children}                                                                                     & \multicolumn{1}{l|}{92 (2.0\%)}                                              & \multicolumn{1}{l|}{70 (2.8\%)}                                               & \multicolumn{1}{l|}{184 (3.3\%)}                                     & \multicolumn{1}{l|}{212 (5.2\%)}                                            & \multicolumn{1}{l|}{131 (3.4\%)}                                    & \multicolumn{1}{l|}{689 (3.3\%)}                                    \\ \hline
\multicolumn{1}{|l|}{Two children}                                                                                               & \multicolumn{1}{l|}{361 (7.9\%)}                                             & \multicolumn{1}{l|}{201 (8.0\%)}                                              & \multicolumn{1}{l|}{537 (9.6\%)}                                     & \multicolumn{1}{l|}{401 (9.8\%)}                                            & \multicolumn{1}{l|}{371 (9.7\%)}                                    & \multicolumn{1}{l|}{1871 (9.1\%)}                                   \\ \hline
\multicolumn{1}{|l|}{number\_marriages}                                                                                          & \multicolumn{1}{l|}{}                                                        & \multicolumn{1}{l|}{}                                                         & \multicolumn{1}{l|}{}                                                & \multicolumn{1}{l|}{}                                                       & \multicolumn{1}{l|}{}                                               & \multicolumn{1}{l|}{}                                               \\ \hline
\multicolumn{1}{|l|}{Mean (SD)}                                                                                                  & \multicolumn{1}{l|}{0.845 (0.607)}                                           & \multicolumn{1}{l|}{0.860 (0.651)}                                            & \multicolumn{1}{l|}{0.820 (0.611)}                                   & \multicolumn{1}{l|}{0.842 (0.606)}                                          & \multicolumn{1}{l|}{0.626 (0.610)}                                  & \multicolumn{1}{l|}{0.799 (0.620)}                                  \\ \hline
Range                                                                                                                            & 0.000 - 4.000                                                                & 0.000 - 4.000                                                                 & 0.000 - 4.000                                                        & 0.000 - 4.000                                                               & 0.000 - 4.000                                                       & 0.000 - 4.000                                                       \\ \hline
\end{longtable}
\end{landscape}

