---
title: "Predicts Individual Life Satiafication by Demographic Characteristics"
author: "Heran Zhou, Xinyu Zhong, Yaqi Feng, Yuhan Gu"
date: "Octobor 19, 2020"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{subfig}
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: false
---

\begin{center} 
github: https://github.com/Kevinzhou0717/STA304-Problem-Set-2
\end{center} 

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(dplyr)
library(survey)
library(pROC)
library(kableExtra)
#library(bookdown)
library(arsenal)
library(gridExtra)
library(grid)
```

```{r dataimport, echo=F, include=F}
gss <- read_csv('gss.csv')
raw_data <- read_csv("AA4uzB6k.csv")
```

# Abstract
Canada has long been recognized as a country with high levels of citizen life satisfaction, and factors related to family are thought to be greatly influential to citizen’s feelings on life. This study is based on the 2017 General Social Survey (“GSS”), with the central theme being “families”, and aims to use the logistic regression model with demographic characteristics to predict the life satisfaction of individuals.  Although there were some biases in life satisfaction as a subjective factor, the results of the model provided evidence for the contribution of gender, income, education, family relationship, and other factors to life satisfaction. Government bodies and interested individuals can use the result to evaluate the effectiveness of current social welfare policies and hence make better judgments.  \par

# Introduction
Family, as the foundation of society, makes unique and irreplaceable contributions to the health of our economy. Today’s family, nonetheless, is becoming increasingly diverse due to changing living standards, diversifying cultures and improving technologies. How modern families and affiliated individuals feel about life under rapid societal changes has become a topic of our wonder. \par
Our goal is to **investigate the influential factors affecting a person’s life satisfaction and the extent of their impacts**. This is done through organizing and analyzing data retrieved from the 31st cycle, focusing on families, of the General Social Survey at Statistics Canada. Details of the dataset will be introduced in the section that follows. In the dataset, we assumed for gender, education, living area, marital status, self-rated health and family income to be the correlated variables that will impact a person’s life satisfaction as a whole and the result is surprising. \par
The sections that follow will elaborate on the basis of data selection, details of the regression model, regression results, discussion of results, model limitations and further improvements. Government bodies can consider the result in the policy-making process to determine which policies to adopt. Interested groups and individuals can use the result to evaluate the effectiveness of current social welfare programs.\par

# Data
We obtained this dataset from the 31st cycle of the General Social Survey (“GSS”) conducted by the Diversity and Sociocultural Statistics at Statistics Canada. This dataset contains 461 variables, derived from the responses on a telephone-based Questionnaire collected from 20,602 respondents. \par
The **sampling method** of this dataset is unique and complex, with stratification, multiple stages of selection and unequal selection probabilities for respondents. To more detail, the **target population** is all persons fifteen years of age and older in Canada, excluding the residents of Yukon, Northwest Territories and Nunavut, as well as full-time residents of institutions. A total of 27 strata were formed by geographic areas, in which 17 are Census Metropolitan Areas (“CMAs”) and the remaining are non-CMAs. \par
The **frame population**, on the other hand, is created with two different components. The first one being the list of telephone numbers in use, both landline and cellular, available to Statistics Canada. The latter would be the Address Register, a list of all dwellings within the ten provinces of interest, used to group together all telephone numbers associated with the same valid address. The **sampling frame** \footnote{Upon collection of responses, the telephone numbers would be grouped into records that consist of the sampling unit on the survey frame. Then, each record in the frame was assigned to a stratum within its province. Lastly, a simple random sample without replacement of records was performed in each stratum.} 
is hence the combination of telephone numbers and the Address Register. \par

The dataset has several **advantages**. Firstly, it comprises a large pool of data, collecting beyond its desired sample size, with a variety of attributes concerning facets relevant to a family navigating through conjugal, family, and work trajectories. Moreover, the responses and information contained in this data set are also very much recent, collected and carefully weighted to represent the entire population. Specifically, each person selected in the sample represents several other persons not in the sample, and the number of persons represented by a given person is determined using a weighting factor of the sampled person. Therefore, this dataset should be a good representation of both the sampled and non-sampled population. \par
However, some **weaknesses** are evident too. The most apparent ones being the sampling and non-sampling error. **Sampling error**, the difference between the estimates obtained from the sample and the results from a complete count taken under similar conditions, appears because the survey is designed to be based on a sample of persons. That is, have the same design and methodology be applied to a complete census, the results might be different. 
**Non-sampling errors**, on the other hand, can happen at every stage too \footnote{Examples include interviewers misunderstanding instructions, respondents making mistakes in answers, errors appearing in inputting, processing and tabulating data, and etc.}. 
However, the most prominent source of non-sampling errors would be non-responses on survey results, both partial and total. The former occurs when respondents fail to answer one or a few questions, whereas the latter occurs when the respondents fail to answer all questions. This may lead to the volunteer bias where the voluntary participants in the study do not represent the entire population. As discussed in the GSS31 user guide published by Statistics Canada, non-respondents tend to be younger males. The non-responses and the resulting unequal distribution of demographic characteristics are handled by adjusting the weight of households who responded to the survey to cover for those who did not. \par
Moreover, aside from the sampling and non-sampling errors, the choice of frame population may limit the target population's ability to represent. As previously stated, the frame population is created through the telephone numbers available to Statistics Canada. Neglecting the fact that there may be contact numbers available to Statistics Canada already, households without telephones were excluded from the survey population. One may argue that this population is minimal, but this conclusion cannot be drawn unless further studies on the demographic group without telephones are done. \par
Additionally, as discussed previously, this survey has its unique and complex design, which could affect the estimation and variance calculations used in common analyses, posing analytical challenges. Also, since the responses from this survey are based on a sample of persons, different figures might be obtained if a complete census had been taken using the same Questionnaire, interviewers, supervisors, processing methods, etc. \par

```{r pairplot, fig.cap="Plot of raw data", out.width=".7\\linewidth", fig.align="center", echo=FALSE}
sub_plot <- raw_data %>% 
  select(agedc,slm_01,sex,prv,region,
         luc_rst,marstat, ehg3_01b,famincg2,
         odr_10,livarr12,uhw_16gr,lmam_01,srh_110) %>% 
  mutate_at(vars(agedc:srh_110), .funs = funs(ifelse(.>=96, NA, .))) 
# Fix the names
sub_plot <- sub_plot %>% 
  rename(age = agedc, feelings_life = slm_01,
         sex = sex, province = prv,
         region = region,pop_center = luc_rst,
         marital_status = marstat,education = ehg3_01b,
         income_family = famincg2,own_rent = odr_10,
         living_arrangement = livarr12,average_hours_worked = uhw_16gr,
         worked_last_week = lmam_01,self_rated_health = srh_110) 
sub_plot <- sub_plot %>%
  select(feelings_life, age, income_family, education, 
         marital_status, living_arrangement, self_rated_health)
sub_plot <- na.omit(sub_plot)
pairs(sub_plot)
```

The raw data was initially filtered, reorganized, and renamed by gss_cleaning.r (Rohan & Sam Caetano, 2020), and the total variable dropped from 461 to 81 by cleaning. Highly correlated variables and variables with high proportions of missing values were excluded during the cleaning process to avoid multicollinearity and to increase model efficiency.As shown in the scatter plot (Figure \@ref(fig:pairplot)), the majority of responses are coded by scale and they are discrete variables.\par 
The questionnaire is detailed and some variables can overlap each other. We pay more attention to variables on family level rather than individual level. In the end, we narrowed our scope to six independent predictor variables of interest. They are gender, education, living area, marital status, self-rated health and family income. After omitting missing values within this scope, the final dataset used for regression analysis contains 19,873 observations.\par

```{r mutat, echo=F, include=F}
# select variable and change variable type
col.names <- colnames(gss[,c(12:24,27:62,64:81)])
gss[,col.names] <- lapply(gss[,col.names], as.factor)
data <- gss %>% 
  select(age, sex, income_family, place_birth_canada, region, is_male,
           education, pop_center, feelings_life, marital_status, 
           living_arrangement, self_rated_health, income_respondent,
           self_rated_mental_health, religion_has_affiliation,
           children_in_household, number_marriages)
data <- na.omit(data)
summary(data)
glimpse(data)
# reduce level of self_rated_health 
data$self_rated_health[data$self_rated_health[]=="Don't know"] <- "Fair"
data$self_rated_health[data$self_rated_health[]=="Very good"] <- "Good"
data$self_rated_health <- droplevels(data$self_rated_health)
# reduce level of education level
levels(data$education)[8:9] <- c("Bachelor or above",
                                  "college / below bachelor level")
data$education[data$education[]=="Bachelor's degree (e.g. B.A., B.Sc., LL.B.)"] <- "Bachelor or above"
data$education[data$education[]=="University certificate, diploma or degree above the bach..."] <- "Bachelor or above"
data$education[data$education[]=="University certificate or diploma below the bachelor's level"] <- "college / below bachelor level"
data$education[data$education[]=="College, CEGEP or other non-university certificate or di..."] <- "college / below bachelor level"
data$education[data$education[]=="Trade certificate or diploma"] <- "college / below bachelor level"
data$education <- droplevels(data$education)
# reduce level of living arrangement
levels(data$living_arrangement)[12:13] <- c("No spouse and children",
                                 "Spouse and children")
data$living_arrangement[data$living_arrangement[]=="No spouse and single child under 25 years of age" ]<-"No spouse and children"
data$living_arrangement[data$living_arrangement[]=="No spouse and single child 25 years of age or older" ]<-"No spouse and children"
data$living_arrangement[data$living_arrangement[]=="No spouse and non-single child(ren)" ]<-"No spouse and children"
data$living_arrangement[data$living_arrangement[]=="Spouse and single child under 25 years of age" ]<-"Spouse and children"
data$living_arrangement[data$living_arrangement[]=="Spouse and single child 25 years of age or older" ]<-"Spouse and children"
data$living_arrangement[data$living_arrangement[]=="Spouse and non-single child(ren)" ]<-"Spouse and children"
data$living_arrangement <- droplevels(data$living_arrangement)
# reduce level of pop_center
levels(data$pop_center)[4] <- c("Rural (non CMA/CA)/Prince Edward Island")
data$pop_center[data$pop_center[]=="Prince Edward Island" ]<-"Rural (non CMA/CA)/Prince Edward Island"
data$pop_center[data$pop_center[]=="Rural areas and small population centres (non CMA/CA)" ]<-"Rural (non CMA/CA)/Prince Edward Island"
data$pop_center <- droplevels(data$pop_center)
# reduce level of income_family
levels(data$income_family)[7] <- "$50,000 to $124,999"
data$income_family[data$income_family[]=="$50,000 to $74,999"]<-"$50,000 to $124,999"
data$income_family[data$income_family[]=="$75,000 to $99,999"]<-"$50,000 to $124,999"
data$income_family[data$income_family[]=="$100,000 to $ 124,999"]<-"$50,000 to $124,999"
data$income_family <- droplevels(data$income_family)
```

```{r response,echo=F, include=F}
#for logistic model, divide feeling_of_life by mean
mean(data$feelings_life)
summary(as.factor(data$feelings_life))
data <- data %>% 
  mutate(life_satisfication = as.factor(ifelse(feelings_life>mean(feelings_life),1,0)))
```

# Model

The most of variables in the dataset is discrete and lack linearity between covariates and response which violate assumption of simple linear regression. Though a linear regression model may be more straightforward and easier to analyse, it lacks linearity between covariates and response and violates the assumption of linear model. Therefore, we have chosen to use logistic regression instead, which is more suitable when analysing multi-characteristic discrete variables. \par
The life satisfaction responses collected in the GSS (2017) were individuals’ self-rated feelings on a scale of 0 to 10, and the average is relatively high. It is unclear how one unit change of life satisfaction will impact a person’s behaviours, hence we divided the life feeling responses by their mean value (8.09), to differentiate between individuals with above-average life satisfactions (indicated by 1) and those without (indicated by 0). The resulting new variable, _**Life_Satisfaction**_, which is an indicator, is the response variable of our model. \par
Under our hypothesis, an improvement in 
education level, family income, marital status or self rated health is set to increase the odds of life satisfaction above average. 
Male is assumed to be more likely to have above average life satisfaction than female, due to gender inequalities at workplace, home, etc. Individuals living in rural areas or Prince Edward Island are more likely to have above average life satisfaction than those living in urban areas, due to a more relaxed lifestyle.\par

The basis of our variable selection is as follows:
For our logistic model, “sex” variable and “is_male” variable do not lead to statistical difference. We selected “sex” for a more straightforward intepretation. 
We assume that an individual’s appetite for a living environment (pop_center) impacts more on his or her life satisfaction than the general geographic region (province or region). 
We consider the special cases such as underaged individuals taking income from their family, who may have above average life satisfactions with no personal income. “Income_respondent” is hence removed from our model. 
We assume that an individual’s physical health will have greater influence on his or her life satisfaction. “self_rated_mental_health” was also removed to avoid multicollinearity. 
“marital_status” is chosen over “living_arrangement” since it is more descriptive and specific. For instance, by living “along” under “living_arrangement”, an individual can be separated, divorced or widowed.\par
Some common demographic characteristics such as age and minority status are not selected due to lack of representative. Others including average hours worked and occupation are excluded from the regression model due to high proportions of  missing values. \par
Then, our basic expression of our model is shown as following:
\[
log(\frac{p}{1-p}) = \beta_0 +\beta_1x_1 +\beta_2x_2 +...+\beta_nx_n + \epsilon
\]
where p represents the probability to have life satisfaction above average. $x_i$(i=1,...,n) correspond to levels of *gender*, *education level*, *living area*, *family income*, *marital status* and *self_rated_health*. (Thus, n = sum of level for each predictor has - number of predictors, since one level will used as based line i logistic model), $\beta_i$(i=2,..,7) are estimate coefficient, $\beta_0$ is intercept, $\epsilon$ is random error.\par
For better representation of data and comprehensive interpretation of the model, we have simplified the classification of certain categorical predictor variables by merging their affiliated categories into new categories. Categories are aggregated as referenced in Appendix: Summary of Category Aggregations (Table \@ref(tab:sumcat)).\par
However, we do recognize that the results and outputs from a logistic regression model is harder to interpret and analyze. The predictions would need to be inferred from odds and exponents, which will be done in the following sections. \par
All analysis of data is done by Rstudio software.\par


```{r analyse,ech=F, include=F}
#split data for validation
set.seed(304)
# 60% observations in train dataset, 40% in test data set
smp_size <- floor(0.6 * nrow(data))
train_ind <- sample(seq_len(nrow(data)), size = smp_size)
train <- data[train_ind, ]
test <- data[-train_ind, ]
# fit logistic model
N=35151728
n=length(train$life_satisfication)
fpc.srs = rep(N, n)
train.srs <- svydesign(id=~1, data=train, fpc=fpc.srs)
train.logit <- svyglm(life_satisfication ~ sex + education + pop_center +
                       marital_status + self_rated_health +income_family, 
                       train.srs, family="binomial")
summary(train.logit) 
# use test dataset to test validity
N=35151728	
n=length(test$life_satisfication)
fpc.srs = rep(N, n)
test.srs <- svydesign(id=~1, data=test, fpc=fpc.srs)
test.logit <- svyglm(life_satisfication ~ sex + education + pop_center +
                       marital_status + self_rated_health + income_family, 
                       test.srs, family="binomial")
summary(test.logit)

#full model
N=35151728
n=length(data$life_satisfication)
fpc.srs = rep(N, n)
data.srs <- svydesign(id=~1, data=data, fpc=fpc.srs)
data.logit <- svyglm(life_satisfication ~ sex + education + pop_center +
                       marital_status + self_rated_health +income_family, 
                       data.srs, family="binomial")
summary(data.logit) 
```

# Result
```{r model}
beta <- coef(data.logit)
SD <-  summary(data.logit)$coef[,2]
p_value = format(summary(data.logit)$coef[,4], scientific = TRUE, digits = 3)
CI <- round(exp(confint(data.logit)),3)
# table of coefficient
kable(cbind(round(exp(beta),3),CI[,1],CI[,2], p_value),
      col.names = c('Estimated', 
                    'Confidence', 'Interval',
                    'P value'),
      booktabs = TRUE,
      caption = "Summary of Model")
```

The final model result indicates that gender, education, living area, marital status, self-rated health and family income are the significant (p value < 0.05) predictors of life satisfaction. In addition, self-rated health, some of education, marital status and family income levels are especially significant (p<0.001). 
The response of logistic model is log odds as described in last section, we did exponential transfer for the estimated coefficient to order to more direct interpretation. The estimated coefficient after exponential calculation, confidence interval, and p-value are summarized in Table \@ref(tab:model).\par
```{r ROC, fig.cap="ROC curve", echo=F}
#ROC curve
roc_p <- predict(data.logit, type = "response")
roc_l <- roc(data$life_satisfication ~ roc_p)
## Setting levels: control = 0, case = 1
## Setting direction: controls < cases
## The True Positive Rate ##
TPR <- roc_l$sensitivities
## The False Positive Rate ##
FPR <- 1 - roc_l$specificities
roc <- data.frame(FPR,TPR)
#ROC curve
ggplot(roc, aes(FPR,TPR)) + 
  geom_line(size = 2, alpha = 0.7,col='red') +
  geom_segment(aes(x = 0, xend = 1, y = 0, yend = 1), linetype="dashed") +
  labs(x = "False Positive Rate (1-Specificity)", 
       y = "True Positive Rate (Sensitivity)") +
  annotate("text", x = 0.75, y = 0.5, vjust = 0, 
           label = paste("AUC =",round(auc(roc_l),2)))
```
In addition, the AUC (area under curve) = 0.68 as the ROC curve (Figure \@ref(fig:ROC)) illustrates that the predictive of the final model is 0.68, which is considered acceptable. Also, as shown in appendix Table \@ref(tab:validation), the model build use test dataset gets similar coefficients of the model as when using the training dataset, so the final model is validated through cross-validation. That is, the model is reasonable valid and predictive.\par

# Discussion
As discussed in previous sections, the data is obtained from the 31st cycle of the General Social Survey (“GSS”) conducted by the Diversity and Sociocultural Statistics at Statistics Canada. The volunteer bias may exist and reweighting was performed to adjust for that. Response variable is also transformed to categorical variable to avoid the unequal distribution of original variable caused by such bias. \par
According to the summary (Table \@ref(tab:model)), the odds of life satisfaction level above average will decrease by about 10% for males than females, increase by 17.8% for individuals living in rural areas or Prince Edward Island than those living in urban or CMA/CA areas. Self rated health is shown as highly significant in determining the admit. Compare with *Excellent*, the odds of life satisfaction level above average will decrease by 60%, 84%, 90% correspond to  is *Good*, *Fair*, *Poor*.\par
Compared with high school and its equivalent education level, the odds of more life satisfaction will increase by 43.7% when education level is less than high school, decrease by 16.9% when education level is bachelor or above. The confidence interval of the coefficient of college / below bachelor level education contains 1 which indicates that there is no significant difference. \par 
As well, compared with family income more than $125,000, the odds of above average life satisfaction will decrease by 28%, 20%, 12% when family income is Less than $25,000, $25,000 to $49,999, $50,000 to $124,999, respectively. \par
In contrast with marital status’ baseline value *divorce*, the odds of more life satisfaction will decrease by 37%, 24.6% when the respondent’s marital status is *separated*and *single*, and increase by 23%, 31%, 75.4% when it is *living common law*, *widowed*, and *married*.\par
The results indicate that living area, family income and self-rated health comply with our hypothesis, whereas gender, education and marital status have brought us surprises. \par
As implied by the results, the increase in family income and the improvement of self-rated health can make an individual more probable to have above average life satisfactions. People living in rural areas or Prince Edward Island are more likely to have outstanding life satisfactions, in contrast with those living in large urban areas. \par
However, the higher an individual’s education level is, the less likely he or she will have life satisfactions above average. This is possibly due to the social structure of Canada. As a developed country, Canada has more skilled workers than unskilled workers. Such imbalance has caused an excess supply of skilled workers and an excess demand for unskilled workers, which has resulted in the competitive job market for undergraduates and high labor cost. \par
Furthermore, females are slightly more likely to have above average life satisfactions than males. The odds will increase by a small difference for females than males. This could possibly imply that the issue of gender inequality is contained well in Canada. \par
Lastly, marital status complies partially with our expectations. People married or living common-law are generally more likely to have above average life satisfactions than people divorced and single or separated people are generally less likely to have above average life satisfactions. However, it is out of our expectations that widowed people have higher odds than the divorced. We have found no good explanation for this phenomenon. It is hard to argue whether “widowed” is an improvement from “divorced”. \par

The model can provide reference to government bodies on the effectiveness of current social welfare policies. For instance, self-rated health is an extremely significant variable which brings significant difference among each of its affiliated categories. This could imply that Canadian social welfare policies should focus on Canadians’ health and the universal healthcare program is potentially a great contributor to Canada’s high average life satisfaction. As well, government bodies, educational institutions and interested individuals can analyze the results on education coefficients to reconsider the necessity of education from a demographic perspective instead of a financial perspective. Universities can also reconsider the justifiability of increasing tuitions. \par

```{r bp, fig.cap="Feelings of life vs. Self rated health", echo=F}
ggplot(data, aes(self_rated_health,feelings_life))+
  geom_boxplot()+
  labs(title="Feelings of life vs. Self rated health")

```
As indicated by the sample boxplot (Figure 3) that measures the relationship between feelings_life and self_rated_health, there are apparent differences between each health category. A clear trend of increasing life satisfaction exists as the respondents’ health condition improves. \par

## Weaknesses
The analysis performed has a few apparent weaknesses.\newline
Firstly, and probably the most apparent, the mean of both variable Feeling_life and Age is somewhat distorted towards the higher end. Note that the variable Feeling_life is ordinal in the dataset, ranging from 0 to 10 inclusive, and its mean is 8.09 when split as indicator variable, leaning toward the higher end. This either suggests that the sampled population has a very positive feeling towards their lives, or that this variable was over-reported during the survey process and cannot be used to represent and predict the population. \par
The high age mean, on the other hand, suggests that the majority of people who responded to the survey are of the older age groups. Therefore, the analysis performed on such respondent demographic composition could have limited representation power on the entire target population. \par
Secondly, as discussed in the previous sections, we omitted numerous variables that have high correlation or high proportions of missing values to avoid multicollinearity and to increase model efficiency. However, some variables that were omitted may be potentially effective and would be logical to consider when evaluating a person’s life satisfaction level. For example, average number of working hours, mental health status and occupation. Excluding them may seem beneficial from the model building perspective, but illogical otherwise. \par

## Next Steps
The following paragraphs will offer some insights into potential next steps for future analyses. \newline
As previously discussed, the frame population of the survey that provided information for the dataset is created with two components, in which the major one is the list of telephone numbers available to Statistics Canada. By the nature of such a frame population, households without a telephone number available to Statistics Canada are omitted from the survey population, hindering the representation ability of the sampled population. Therefore, we would suggest conducting a follow-up survey using different approaches to cover as much of the target population as possible. An alternative approach could be a computer-assisted personal interviewing (CAPI), or computer-assisted self-interviewing (CASI), both of which would allow a broader exposure to the target population via digital technology. The use of digital technology may also enable the follow-up survey to reach younger respondents, as the age mean of the survey presented in the dataset is somewhat distorted towards the higher end. Note that the follow-up surveys could narrow the general survey topic down to analysis-specific ones to increase the amount of relevant data available for the analysis. \par

Additionally, other data analysis techniques could be used. For example, software like Python could be used in addition to R, as done in previous sections, to allow for a more concise and detailed analysis. Also, data could be inputted using automated machines to reduce manual input errors.  \par

\newpage

# References
1. Alexander, R., & Caetano, S. (2020, 10 07). gss_cleaning.R.
2. Beaupre, P. (2020). General Social Survey Cycle 31: Families, Public Use
  Microdata File Documentation and User's Guide. Ottawa: Authority of the Minister    responsible for Statistics Canada.
3. Statistics Canada. 2017. Census Profile. 2016 Census. Statistics Canada Catalogue no. 98-316-X2016001. Ottawa. Released November 29, 2017. https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/index.cfm?Lang=E

4. T. Lumley (2020) "survey: analysis of complex survey samples". R package
  version 4.0.

5. Xavier Robin, Natacha Turck, Alexandre Hainard, Natalia Tiberti, Frédérique
  Lisacek, Jean-Charles Sanchez and Markus Müller (2011). pROC: an
  open-source package for R and S+ to analyze and compare ROC curves. BMC
  Bioinformatics, 12, p. 77.  DOI: 10.1186/1471-2105-12-77
  <http://www.biomedcentral.com/1471-2105/12/77/>

6. Hao Zhu (2020). kableExtra: Construct Complex Table with 'kable' and Pipe
  Syntax. http://haozhu233.github.io/kableExtra/,
  https://github.com/haozhu233/kableExtra.

7. Ethan Heinzen, Jason Sinnwell, Elizabeth Atkinson, Tina Gunderson and
  Gregory Dougherty (2020). arsenal: An Arsenal of 'R' Functions for
  Large-Scale Statistical Summaries. https://github.com/mayoverse/arsenal,
  https://cran.r-project.org/package=arsenal,
  https://mayoverse.github.io/arsenal/.

\newpage

# Appendix

```{r validation}
beta1 <- coef(train.logit)
beta2 <- coef(test.logit)
p_value = format(summary(train.logit)$coef[,4], scientific = TRUE, digits = 4)
# table of coefficient
kable(cbind(round(exp(beta2),3), round(exp(beta1),3), p_value),
      col.names = c('test','train','P value'),
      booktabs = TRUE,
      caption = "Cross Validation of Model")
```


```{r sumtable, echo = F,  results="asis"}
tt <- gss %>% 
  select(age, sex, feelings_life, place_birth_canada,  
         vis_minority, citizenship_status, own_rent,income_family, 
         education, pop_center, marital_status, 
         living_arrangement, self_rated_health, 
         self_rated_mental_health, religion_has_affiliation,
         children_in_household, number_marriages)
table_one <- tableby(gss$region ~ ., data = tt)
summary(table_one, title = "Summary of Data")

```

\newpage

\begin{longtable}[c]{|l|l|l|}
\caption{Summary of Category Aggregations}
\label{tab:sumcat}\\
\hline
Variable Names & \textbf{Original Categories} & \textbf{Aggregated Categories} \\ \hline
\endfirsthead
%
\endhead
%
\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Gender \\ (“sex”)\end{tabular}}} & Male & Male \\ \cline{2-3} 
 & Female & Female \\ \hline
\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Education Level \\ (“education”)\end{tabular}}} & Bachelor’s degree & \multirow{2}{*}{Bachelor or above} \\ \cline{2-2}
 & \begin{tabular}[c]{@{}l@{}}University certificate, diploma or \\ degree above the bach…\end{tabular} &  \\ \cline{2-3} 
 & \begin{tabular}[c]{@{}l@{}}University certificate, diploma or \\ degree below the bachelor’s level\end{tabular} & \multirow{3}{*}{college/below bachelor level} \\ \cline{2-2}
 & \begin{tabular}[c]{@{}l@{}}College, CEGEP or \\ other non-university certificate or di…\end{tabular} &  \\ \cline{2-2}
 & Trade certificate or diploma &  \\ \cline{2-3} 
 & \begin{tabular}[c]{@{}l@{}}High school diploma or \\ a high school equivalency certificate\end{tabular} & \begin{tabular}[c]{@{}l@{}}High school diploma or \\ a high school equivalency certificate\end{tabular} \\ \hline
\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Living area \\ (“pop\_center”)\end{tabular}}} & \begin{tabular}[c]{@{}l@{}}Rural areas and \\ small population centres\\ (non CMA/CA)\end{tabular} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Rural areas (non CMA/CA) or \\ Prince Edward Island\end{tabular}} \\ \cline{2-2}
 & Prince Edward Island &  \\ \cline{2-3} 
 & \begin{tabular}[c]{@{}l@{}}Larger urban population centres \\ (CMA/CA)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Larger urban population centres \\ (CMA/CA)\end{tabular} \\ \hline
\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Family income \\ (“income\_family”)\end{tabular}}} & Less than \$25,000 & Less than \$25,000 \\ \cline{2-3} 
 & $25,000 to $49,999 & 25,000 to \$49,999 \\ \cline{2-3} 
 & $50,000 to $74,999 & \multirow{3}{*}{$50,000 to $124,999} \\ \cline{2-2}
 & $75,000 to $99,999 &  \\ \cline{2-2}
 & $100,000 to $124,999 &  \\ \cline{2-3} 
 & \$125,000 and more & above \$125,000 \\ \hline
\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Marital Status\\ (“marital\_status”)\end{tabular}}} & Single, never married & Single, never married \\ \cline{2-3} 
 & Married & Married \\ \cline{2-3} 
 & Living common-law & Living common-law \\ \cline{2-3} 
 & Separated & Separated \\ \cline{2-3} 
 & Widowed & Widowed \\ \cline{2-3} 
 & Divorced & Divorced \\ \hline
\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Self Rated Health\\ (“self\_rated\_health”)\end{tabular}}} & Excellent & Excellent \\ \cline{2-3} 
 & Very good & \multirow{2}{*}{Good} \\ \cline{2-2}
 & Good &  \\ \cline{2-3} 
 & Fair & \multirow{2}{*}{Fair} \\ \cline{2-2}
 & Don't know &  \\ \cline{2-3} 
 & Poor & Poor \\ \hline
\end{longtable}